DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-29 paper/background.tex
still revising (unsatisfactory.)
background revision (WIP)

(1) AI and Robotics
- explosion of AI
- in particular, application of DNN in perception and control of robotics systems.
- end-to-end control is a promising technique.
  levine's publications?
- examples: nvidia's DAVE-II prototype, forest navigating drone
challenge problem: computing at low cost?

%% UPenn's f1/10 BOM: $3,628.37	
%% http://f1tenth.org/
%% http://selfdrivingcars.mit.edu/
%% http://fast.scripts.mit.edu/racecar/
%% https://github.com/mit-racecar

(2) Multicore SBCs
- computing has been a obstacle.
- performance, but also constraints size, weight, and power as well as
cost senstive nature of industries including automtive.
- many new embeded computing platforms emerged: affordable and
powerful. raspberry pi, nvidia's embedded platforms tout their
superiority in GPU based acceleration of the AI tasks.

>>>>

\subsection{Deep End-to-End Control}
End-to-end training of deep neural network models is an active
research area in the fields of AI~\cite{Levine2016}.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/endtoend}
  \caption{Standard robotics control vs. DNN based end-to-end
    control. \fixme{figure must be redrawn}}
\end{figure}

- explosion of AI
- in particular, application of DNN in perception and control of robotics systems.
- end-to-end control is a promising technique.
  levine's publications?
- examples: nvidia's DAVE-II prototype, forest navigating drone
challenge problem: computing at low cost?

%% UPenn's f1/10 BOM: $3,628.37	
%% http://f1tenth.org/
%% http://selfdrivingcars.mit.edu/
%% http://fast.scripts.mit.edu/racecar/
%% https://github.com/mit-racecar
%% https://mit-racecar.github.io/

\subsection{Embedded Multicore Single-Board-Computers}

- computing has been a obstacle.
- performance, but also constraints size, weight, and power as well as
cost senstive nature of industries including automtive.
- many new embeded computing platforms emerged: affordable and
powerful. raspberry pi, nvidia's embedded platforms tout their
superiority in GPU based acceleration of the AI tasks.

### 2017-09-29 paper/intro.tex
background revision (WIP)

% our goals
Instead, we want to build a low cost testbed that still employs the
state-of-the art AI technologies. Specifically, we focus on a deep
convolutional neural network (CNN) based end-to-end control system,
which was developed for a real self-driving car, NVIDIA
DAVE-2~\cite{Bojarski2016}, and use the same moethodology on a
smaller, safer and less costly setup. In developing the testbed, our
goals are (1) analyze real-time issues in DNN based end-to-end
control; (2) evalute real-time performance of contemporarly embedded
multicore platforms for the AI workloads.

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$200 in total).
The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}. 
The network has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is identifical to that of NVIDIA's DAVE-2
self-driving car~\cite{Bojarski2016}, which uses much more powerful
computer (NVIDIA's automotive specialized DRIV-PX
computer~\cite{drivepx}) than the Raspberry Pi~3.
We chose to use the Pi 3 not only because of its
affordability but also because it is representative
of today's mainstream low-end multicore platforms, found in
smartphones and other embedded devices.

@@

% how we trained (maybe moved to a later section)
We follow the standard supervised learning methodology to train the
system to follow tracks on the ground. We collect data for
taining and validation by manually  
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
equips a NVIDIA GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform interference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each inference operation must
be completed within the desired control period. (e.g., 50ms period for
20Hz control frequency.)
% how we evaluated (in terms real-time performance)

>>>>

% our goals
Instead, we want to build a low cost testbed that still employs the
state-of-the art AI technologies. Specifically, we focus on a deep
convolutional neural network (CNN) based end-to-end control system,
which was developed for a real self-driving car, NVIDIA
DAVE-2~\cite{Bojarski2016}, and use the same moethodology on a
smaller, safer and less costly setup. In developing the testbed, our
goals are (1) to analyze real-time issues in DNN based end-to-end
control; (2) to evalute real-time performance of contemporarly embedded
multicore platforms for the AI workloads.

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$100 in total).
The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}. 
The network has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is identifical to that of NVIDIA's DAVE-2
self-driving car~\cite{Bojarski2016}, which uses much more powerful
computer (Drive PX computer~\cite{drivepx}) than Raspberry Pi~3.
We chose to use Pi 3 not only because of its
affordability but also because it is representative
of today's mainstream low-end embedded multicore platforms, found in
smartphones and other embedded devices.

@@

% how we trained (maybe moved to a later section)
We apply a standard imitation learning methodology to train the cat to
follow tracks on the ground. We collect data for 
taining and validation by manually  
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
equips a NVIDIA GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform interference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each inference operation must
be completed within the desired control period. (e.g., 50ms period for
20Hz control frequency.)
% how we evaluated (in terms real-time performance)
